Data Analysis and Modeling of Teen Vaccination Surveys

### 2024-04-17 code/analysis-code/analysis2.5.qmd
updated analysis

final_rf <- finalize_model( # select the best model based on roc_auc
  tune_spec,
  best_auc
)
# fit the tuned model
rf_rec <- recipe(P_UTDHPV ~ AGE + SEX + STATE + INS_STAT2_I + INCQ298A + INS_BREAK_I + INCPOV1 + RACEETHK + EDUC1 + LANGUAGE + MOBIL_1 + RENT_OWN + FACILITY, data = train_data) # use full model as recipe for the random forest model

rf_fit <- rf_workflow%>%
  fit(data = train_data)%>% # use the workflow to fit the rf model to the data
print(rf_fit)
```
The final random forest model was selected to optimize roc_auc, but it also has a fairly high accuracy. We can use
```{r}
final_rf_fit <- fit(final_rf, data = train_data)

```

```{r}
# RF model compared to single predictor model
## Create a single model
rf_rec_null <- recipe(P_UTDHPV ~ SEX, data = train_data) # specify the model with a recipe; I could not get a null model to work so I used one predictor as a minimal model for comparison

@@

rf_workflow_mull <- workflow() %>% # create workflow with the recipe and spec
  add_recipe(rf_rec_null) %>% 
  add_model(rf_spec_null)

@@

# Get predictions for tuned model
rf_tuned <- augment(rf_res, train_data)

# Get predictions for first fit model

# Create combined data frame

# Plot tuned model, first fit, and single predictor model together

```
```{r}
# RF model performance with cross validation

```

>>>>

final_rf <- finalize_model( # select the best model based on roc_auc
  tune_spec,
  best_auc
)

# fit the tuned model
rf_rec <- recipe(P_UTDHPV ~ AGE + SEX + STATE + INS_STAT2_I + INCQ298A + INS_BREAK_I + INCPOV1 + RACEETHK + EDUC1 + LANGUAGE + MOBIL_1 + RENT_OWN + FACILITY, data = train_data) # use full model as recipe for the random forest model

rf_tune_workflow <- workflow() %>% # create workflow for rf model
  add_recipe(rf_rec)%>% # apply recipe
  add_model(final_rf) # apply model

rf_tune_fit <- rf_tune_workflow%>%
  fit(data = train_data)%>% # use the workflow to fit the rf model to the data
print(rf_fit)
```
The final random forest model was selected to optimize roc_auc, but it also has a fairly high accuracy. We can use
```{r}
# make predictions
rf_tuned_aug <- augment(rf_tune_fit, train_data)

# find metrics for tuned fit
tuned_fit_metrics <- metrics(truth = P_UTDHPV, estimate = .pred_class, data = rf_tuned_aug) # calculate metrics for first fit
print(tuned_fit_metrics)
```
The F1 measure has improved significantly, to 0.86 and the accuracy increased slightly, to 0.95.

Now I will compare the model will the a single predictor model and the original fit to verify that there is improvement in the predicitons made.
```{r}
# RF model compared to single predictor model
## Create a single model
rf_rec_null <- recipe(P_UTDHPV ~ SEX, data = train_data) # specify the model with a recipe; I could not get a null model to work so I used one predictor as a minimal model for comparison

@@

rf_workflow_null <- workflow() %>% # create workflow with the recipe and spec
  add_recipe(rf_rec_null) %>% 
  add_model(rf_spec_null)

@@

# Get predictions from single predictor model
rf_null_aug <- augment(rf_fit_null, train_data)
```
Note to future self: You cannot plot the models on coordinates because the predictions are classifications (not coninuous). Find another visual representation to compare the models.

### 2024-04-17 code/analysis-code/analysis4.qmd
updated analysis

---
title: "Data Analysis and Modeling of Teen Vaccination Surveys"
date: '`r format(Sys.Date())`'
Author: Kelly Cao and Rachel Robertson
output: html_document
editor: 
  markdown: 
    wrap: sentence
---
# Ridge Regression

>>>>

---
title: "Data Analysis and Modeling of Teen Vaccination Surveys"
date: '`r format(Sys.Date())`'
Author: Kelly Cao and Rachel Robertson
output: html_document
editor: 
  markdown: 
    wrap: sentence
---
# Finding Best Model
Comparing the previous three models used in analysis1.qmd, analysis2.5.qmd, and analysis4.qmd. These models include : general logistic regression model, Random Forest regression model, and LASSO regression model.

# Summary of the predictions and Metrics

# Test Data
